\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electronic Systems

### 2023-07-19 TilingProjectDraft/tilingProject.tex
correct figures

\title{\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electronic Systems}
\author{Abhirup Mukherjee, N.S. Vidhyadhiraja, A. Taraphder, Siddhartha Lal}
% \affil{Indian Institute of Science Education and Research Kolkata, Mohanpur}
\date{\today}

@@

Previously, we have worked out the grounstate phases of a single-impurity model with an interacting bath:
\begin{equation}\begin{aligned}
	\label{siam_attr}
	\mathcal{H}_\text{aux} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2 
\end{aligned}\end{equation}

@@

As mentioned before, no chemical potential \(\mu\) is generated becuase the auxiliary model was at half-filling, both in the impurity as well as in the bath. We can change the chemical potential by introducing two terms:
\begin{equation}\begin{aligned}
	\eta \sum_\sigma\left(n_{d\sigma} - \frac{1}{2}\right), \mu \sum_{i,\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right)
\end{aligned}\end{equation}
The first term is the particle-hole asymmetry term, and tuning that term moves the impurity away from half-filling. The second term is the usual chemical potential in the bath. Introducing these terms in the auxiliary model changes the bulk model into:
\begin{equation}\begin{aligned}
	\mathcal{H}_{H-H} = -\frac{1}{2}U_\text{H-H} \sum_{i} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \frac{1}{\mathcal{W}}t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{\mathcal{W}}J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j + \mu_\text{H-H}\sum_{i\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right) 
\end{aligned}\end{equation}
The only change is the generation of the last term. The mappings between the existing parameters and their auxiliary model counterparts remain the same, while \(\mu_\text{H-H}\) is given by
\begin{equation}\begin{aligned}
	\mu_\text{H-H} = \eta + \left(N-1\right) \mu
\end{aligned}\end{equation}
In the discussion henceforth, we will assume all the models are at half-filling. We will come back to the doped case at a later point in time.

@@

\(\vec R_0\) is the origin of the lattice, and \(N\) is the number of lattice sites. The uniform piece \(\sum_{i}\mathcal{H}_\text{aux}(\vec R_0)\) acts as the "center-of-mass" Hamiltonian - it responds to spectral flow brought about by changes in boundary conditions. The other piece acts as a "relative motion" Hamiltonian and is insensitive to changes in the boundary conditions, because any spectral flow of the auxiliary model Hamiltonians gets cancelled out in the difference operation. While the COM Hamiltonian is a thermodynamically large object, the number of terms in teh difference piece is only of the order of unity (the sum over \(\vec R_i\) is cancelled out by the \(1/N\) factor). We can therefore expand the exponential in the ratio of the relative piece to the COM piece:

@@

Similar expressions hold for non-local correlation functions.
\begin{equation}\begin{aligned}
	\label{nonlocal_correlation}
	&\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) | \Psi_\text{gs}} \\
	=& \frac{1}{4}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) + \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + 2\vec a) + \mathcal{O}_1(\vec R_0 - \vec a) \mathcal{O}_2(\vec R_0) + \mathcal{O}_1(\vec R_0 - 2\vec a) \mathcal{O}_2(\vec R_0 - \vec a) | \Psi_\text{gs}}\right]\\
	\simeq& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) + \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + 2\vec a) | \psi_\text{aux}(\vec R_0, \vec a)} \right. \\
	      &\left.\braket{\psi_\text{aux}(\vec R_0, -\vec a) | \mathcal{O}_1(\vec R_0 - \vec a) \mathcal{O}_2(\vec R_0) + \mathcal{O}_1(\vec R_0 - 2\vec a) \mathcal{O}_2(\vec R_0 - \vec a) | \psi_\text{aux}(\vec R_0, -\vec a)}\right]\\
	=& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right]
\end{aligned}\end{equation}
In the first equation, the first two terms were introduced to incorporate effects arisingfrom the bath zeroth and first sites (guided by the dynamics of the transition in the underlying extended Anderson model), while the last two terms were introduced to symmetrise the effects of choosing \(\vec R_0\) as \(d\) and \(\vec R_0 + \vec a\) as \(z\), and not other way round. The argument \((1)\) in the operators indicate that theu act at the first site of the bath (beyond the bath zeroth site).

The next-nearest correlation function is relatively simpler, becuase only those terms contribute that involve both the impurity as well as the first site. If \(\vec a^\prime\) denotes the relative vector between a given site and one of its next-nearest neighbours, we can write
\begin{equation}\begin{aligned}
	\label{nnn_correlation}
	\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a^\prime) | \Psi_\text{gs}} =& \frac{1}{2}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a^\prime) + \mathcal{O}_1(\vec R_0 - \vec a^\prime) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}}\right]\\
	=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right]
\end{aligned}\end{equation}

@@

The momentum space Greens function can be expressed as a Fourier transform of the real space Greens functions:
\begin{equation}\begin{aligned}
	G_{H-H} (\vec k, \omega) = \frac{1}{N}\sum_{\vec r, \vec r_j}e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_{H-H} (|\vec{r_i} - \vec {r_j}|, \omega)
\end{aligned}\end{equation}
where $\vec{r_i}$ is the position vector of a particular lattice site. Because of translation invariance, the real space Greens function depends only on the relative vector between any two sites. As a result, $\vec r=0$ gives the local Greens function, $|\vec r|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing). Given that our auxiliary model shows an emergent self-consistency on the impurity site and on the link between the impurity and the zeroth site, we approximate the \(k-\)space Greens functions from the local and nearest-neighbour contributions, by usingthe mapping between the bulk Greens function \(G\) and auxiliary model Greens functions \(\mathcal{G}\)(eq.~\ref{greens_func_relation}):
\begin{equation}\begin{aligned}
	G_{H-H} (\vec k, \omega) \simeq \frac{1}{N}\sum_{\vec{r_i} = \vec {r_j}}\left(G_{H-H} (\omega)\right) _\text{loc} + \frac{1}{N}\sum_{|\vec{r_i} - \vec {r_j}|=a} e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}\left(G_{H-H} (\omega)\right)_\text{n-n}
\end{aligned}\end{equation}
The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, \mathcal{W}\right]\right\}$.
\begin{equation}\begin{aligned}
	\label{k_Gf_siam}
	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^{\mathcal{W}} e^{i \vec{k}\cdot\vec {a_i}} = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{G}_{dd}(\omega) + \frac{1}{\mathcal{W}}\xi_{\vec k}\mathcal{G}_{dz}(\omega) \right]~,
\end{aligned}\end{equation}
where we defined \(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\), it being essentially the disperson in units of the hopping strength \(t\). For example, on a d-dimensional hypercubic lattice, we obtain
\begin{equation}\begin{aligned}
	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i~,
\end{aligned}\end{equation}
leading to \(2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}\) on a 2D square lattice.

@@

\section{Correlation functions in momentum space}
Similar to Greens functions, our formalism also allows calculating \(k-\)space correlation functions \(\chi(\vec q)\) from knowledge of local and nearst-neighbour correlations \(\chi_\text{loc}\) and \(\chi_\text{nn}\). This is seen by Fourier transforming a generic real-space correlation function \(\chi(\vec r)\) corresponding to the operator \(\mathcal{O}\):
\begin{equation}\begin{aligned}
	\chi(\vec r) = \left<\mathcal{O}_1 (\vec R + \vec r) \mathcal{O}_2(\vec R)\right> = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot \vec r}e^{i \left(\vec k + \vec q\right) \cdot \vec R}\left<\mathcal{O}_1 (\vec q) \mathcal{O}_2(\vec k)\right>
\end{aligned}\end{equation}
Since the response should not depend on \(\vec R\) (owing to translation invariance), we have
\begin{equation}\begin{aligned}
	\chi(\vec r) = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot \vec r}e^{i \left(\vec k + \vec q\right) \cdot \vec R}\delta_{\vec k + \vec q, 0}\left<\mathcal{O}_1 (\vec q) \mathcal{O}_2(\vec k)\right> = \frac{1}{N}\sum_{\vec k} e^{-i \vec k \cdot \vec r}\left<\mathcal{O}_1 (-\vec k) \mathcal{O}_2(\vec k)\right>
\end{aligned}\end{equation}
By inverting the Fourier transform, we therefore get
\begin{equation}\begin{aligned}
	\chi(\vec k) &\equiv \left<\mathcal{O}_1 (-\vec k) \mathcal{O}_2(\vec k)\right> = \sum_{\vec r}e^{i \vec{k}\cdot\vec{r}} \chi(\vec r) \simeq \chi_\text{loc} + \xi_{\vec k} \chi_\text{nn} + \Xi_{\vec k}\chi_\text{nnn}~,
\end{aligned}\end{equation}
where \(\chi_\text{loc},\chi_\text{nn},\chi_\text{nnn}\) are local, nearest-neighbour and next-nearest-neighbour correlation functions, with dispersions \(\xi_{\vec k} = 2\left[\cos(k_x a) + \cos\left(k_y a\right)\right] \) and \(\Xi_{\vec k} = 2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right] \). Following eqs.~\ref{local_correlation} through \ref{nnn_correlation}, these can be cast into impurity model correlation functions:
\begin{equation}\begin{aligned}
	\chi(\vec k)=& \frac{1}{2\lambda_{\vec k_0}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{W}}\braket{\mathcal{O}_1(z) \mathcal{O}_2(z)}_\text{aux}\right]\\
		    &+ \frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right] \\
		    &+ \frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right] 
\end{aligned}\end{equation}

@@

In Figs.~\ref{spin_kspace},\ref{charge_kspace} and \ref{pair_kspace}, we show the momentum dependence of two-particle correlation functions. In every figure, each panel shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\). Moving from the left panel to the right is equivalent to moving upwards in the top right quadrant of the first Brillouin zone. In each panel, moving upwards amounts to tuning the system towards the transition. The spin-spin correlations (in Fig.~\ref{spin_kspace}) are large near the \(\vec k = \left( 0,0 \right) \) point, presumably because of the dominance of the Kondo cloud at long wavelengths. They vanish in the local moment phase (flat blue region near the top). The charge and pairing correlations (Figs.~\ref{charge_kspace} and \ref{pair_kspace}) disappear as the system moves into the Kondo regime, but reappear exactly at the transition. This is tied to the non-Fermi liquid theory at the QCP, as seen in the auxiliary model.
\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{spin_kspace_all.pdf}
\caption{Momentum dependence of spin-spin correlation \(\left<\vec{S}_{-\vec k}\cdot\vec{S}_{\vec k} \right>\). Each frame shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\). Moving from the left figure to the right figure is equivalent to moving upwards in the top right quadrant of the first Brillouin zone. In each figure, moving upwards amounts to tuning the system towards the transition. The flat blue region at the top is the local moment phase, void of any non-local correlations.}
\label{spin_kspace}
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{charge_kspace_all.pdf}
\caption{Momentum dependence of charge-charge correlation \(\left<\vec{C}_{-\vec k}\cdot\vec{C}_{\vec k} \right>\), where \(\vec C\) is the charge isospin associated with the doublet formed by the doublon and holon states. Each frame shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\). Moving from the left figure to the right figure is equivalent to moving upwards in the top right quadrant of the first Brillouin zone. In each figure, moving upwards amounts to tuning the system towards the transition. The flat blue region at the top is the local moment phase, void of any non-local correlations.}
\label{charge_kspace}
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{pair_kspace_all.pdf}
\caption{Momentum dependence of pairing correlation \(\left<c^\dagger_{-k\uparrow}c^\dagger_{-k\downarrow}c_{k\downarrow}c_{k\uparrow}\right>\). Each frame shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\). Moving from the left figure to the right figure is equivalent to moving upwards in the top right quadrant of the first Brillouin zone. In each figure, moving upwards amounts to tuning the system towards the transition. The flat blue region at the top is the local moment phase, void of any non-local correlations.}
\label{pair_kspace}
\end{figure}

>>>>

\title{\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electronic Systems}
\author{Abhirup Mukherjee, N.S. Vidhyadhiraja, A. Taraphder, Siddhartha Lal}
\date{\today}

@@

Previously, we have worked out the ground-state phases of a single-impurity model with an interacting bath:
\begin{equation}\begin{aligned}
	\label{siam_attr}
	\mathcal{H}_\text{aux} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2 
\end{aligned}\end{equation}

@@

As mentioned before, no chemical potential \(\mu\) is generated because the auxiliary model was at half-filling, both in the impurity as well as in the bath. We can change the chemical potential by introducing two terms:
\begin{equation}\begin{aligned}
	\eta \sum_\sigma\left(n_{d\sigma} - \frac{1}{2}\right), \mu \sum_{i,\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right)
\end{aligned}\end{equation}
The first term is the particle-hole asymmetry term, and tuning that term moves the impurity away from half-filling. The second term is the usual chemical potential in the bath. Introducing these terms in the auxiliary model changes the bulk model into:
\begin{equation}\begin{aligned}
	\mathcal{H}_{H-H} = -\frac{1}{2}U_\text{H-H} \sum_{i} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \frac{1}{\mathcal{W}}t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{\mathcal{W}}J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j + \mu_\text{H-H}\sum_{i\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right) 
\end{aligned}\end{equation}
The only change is the generation of the last term. The mappings between the existing parameters and their auxiliary model counterparts remain the same, while \(\mu_\text{H-H}\) is given by
\begin{equation}\begin{aligned}
	\mu_\text{H-H} = \eta + \left(N-1\right) \mu
\end{aligned}\end{equation}
In the discussion henceforth, we will assume all the models are at half-filling. We will come back to the doped case at a later point in time.

@@

\(\vec R_0\) is the origin of the lattice, and \(N\) is the number of lattice sites. The uniform piece \(\sum_{i}\mathcal{H}_\text{aux}(\vec R_0)\) acts as the ``center-of-mass" Hamiltonian - it responds to spectral flow brought about by changes in boundary conditions. The other piece acts as a "relative motion" Hamiltonian and is insensitive to changes in the boundary conditions, because any spectral flow of the auxiliary model Hamiltonians gets cancelled out in the difference operation. While the COM Hamiltonian is a thermodynamically large object, the number of terms in the difference piece is of the order of unity (the sum over \(\vec R_i\) is cancelled out by the \(1/N\) factor). We can therefore expand the exponential in the ratio of the relative piece to the COM piece:

@@

Similar expressions hold for non-local correlation functions.
\begin{equation}\begin{aligned}
	\label{nonlocal_correlation}
	&\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) | \Psi_\text{gs}} \\
	=& \frac{1}{4}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) + \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + 2\vec a) + \mathcal{O}_1(\vec R_0 - \vec a) \mathcal{O}_2(\vec R_0) + \mathcal{O}_1(\vec R_0 - 2\vec a) \mathcal{O}_2(\vec R_0 - \vec a) | \Psi_\text{gs}}\right]\\
	\simeq& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) + \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + 2\vec a) | \psi_\text{aux}(\vec R_0, \vec a)} \right. \\
	      &\left.\braket{\psi_\text{aux}(\vec R_0, -\vec a) | \mathcal{O}_1(\vec R_0 - \vec a) \mathcal{O}_2(\vec R_0) + \mathcal{O}_1(\vec R_0 - 2\vec a) \mathcal{O}_2(\vec R_0 - \vec a) | \psi_\text{aux}(\vec R_0, -\vec a)}\right]\\
	=& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right]
\end{aligned}\end{equation}
In the first equation, the first two terms were introduced to incorporate effects arising from the bath zeroth and first sites (guided by the dynamics of the transition in the underlying extended Anderson model), while the last two terms were introduced to symmetrise the effects of choosing \(\vec R_0\) as \(d\) and \(\vec R_0 + \vec a\) as \(z\), and not other way round. The argument \((1)\) in the operators indicate that they act at the first site of the bath (beyond the bath zeroth site).

The next-nearest correlation function is relatively simpler, because only those terms contribute that involve both the impurity as well as the first site. If \(\vec a^\prime\) denotes the relative vector between a given site and one of its next-nearest neighbours, we can write
\begin{equation}\begin{aligned}
	\label{nnn_correlation}
	\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a^\prime) | \Psi_\text{gs}} =& \frac{1}{2}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a^\prime) + \mathcal{O}_1(\vec R_0 - \vec a^\prime) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}}\right]\\
	=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right]
\end{aligned}\end{equation}

@@

The momentum space Greens function can be expressed as a Fourier transform of the real space Greens functions:
\begin{equation}\begin{aligned}
	G_{H-H} (\vec k, \omega) = \frac{1}{N}\sum_{\vec r, \vec r_j}e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_{H-H} (|\vec{r_i} - \vec {r_j}|, \omega)
\end{aligned}\end{equation}
where $\vec{r_i}$ is the position vector of a particular lattice site. Because of translation invariance, the real space Greens function depends only on the relative vector between any two sites. As a result, $\vec r=0$ gives the local Greens function, $|\vec r|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing). Given that our auxiliary model shows an emergent self-consistency on the impurity site and on the link between the impurity and the zeroth site, we approximate the \(k-\)space Greens functions from the local and nearest-neighbour contributions, by using the mapping between the bulk Greens function \(G\) and auxiliary model Greens functions \(\mathcal{G}\)(eq.~\ref{greens_func_relation}):
\begin{equation}\begin{aligned}
	G_{H-H} (\vec k, \omega) \simeq \frac{1}{N}\sum_{\vec{r_i} = \vec {r_j}}\left(G_{H-H} (\omega)\right) _\text{loc} + \frac{1}{N}\sum_{|\vec{r_i} - \vec {r_j}|=a} e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}\left(G_{H-H} (\omega)\right)_\text{n-n}
\end{aligned}\end{equation}
The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, \mathcal{W}\right]\right\}$.
\begin{equation}\begin{aligned}
	\label{k_Gf_siam}
	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^{\mathcal{W}} e^{i \vec{k}\cdot\vec {a_i}} = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{G}_{dd}(\omega) + \frac{1}{\mathcal{W}}\xi_{\vec k}\mathcal{G}_{dz}(\omega) \right]~,
\end{aligned}\end{equation}
where we defined \(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\), it being essentially the dispersion in units of the hopping strength \(t\). For example, on a d-dimensional hypercubic lattice, we obtain
\begin{equation}\begin{aligned}
	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i~,
\end{aligned}\end{equation}
leading to \(2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}\) on a 2D square lattice.

@@

\section{Correlation functions in momentum space}
Similar to Greens functions, our formalism also allows calculating \(k-\)space correlation functions \(\chi(\vec q)\) from knowledge of local and nearest-neighbour correlations \(\chi_\text{loc}\) and \(\chi_\text{nn}\). This is seen by Fourier transforming a generic real-space correlation function \(\chi(\vec r)\) corresponding to the operator \(\mathcal{O}\):
\begin{equation}\begin{aligned}
	\chi(\vec r) = \left<\mathcal{O}_1 (\vec R + \vec r) \mathcal{O}_2(\vec R)\right> = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot \vec r}e^{i \left(\vec k + \vec q\right) \cdot \vec R}\left<\mathcal{O}_1 (\vec q) \mathcal{O}_2(\vec k)\right>
\end{aligned}\end{equation}
Since the response should not depend on \(\vec R\) (owing to translation invariance), we have
\begin{equation}\begin{aligned}
	\chi(\vec r) = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot \vec r}e^{i \left(\vec k + \vec q\right) \cdot \vec R}\delta_{\vec k + \vec q, 0}\left<\mathcal{O}_1 (\vec q) \mathcal{O}_2(\vec k)\right> = \frac{1}{N}\sum_{\vec k} e^{-i \vec k \cdot \vec r}\left<\mathcal{O}_1 (-\vec k) \mathcal{O}_2(\vec k)\right>
\end{aligned}\end{equation}
By inverting the Fourier transform, we therefore get
\begin{equation}\begin{aligned}
	\chi(\vec k) &\equiv \left<\mathcal{O}_1 (-\vec k) \mathcal{O}_2(\vec k)\right> = \sum_{\vec r}e^{i \vec{k}\cdot\vec{r}} \chi(\vec r) \simeq \chi_\text{loc} + \xi_{\vec k} \chi_\text{nn} + \Xi_{\vec k}\chi_\text{nnn}~,
\end{aligned}\end{equation}
where \(\chi_\text{loc},\chi_\text{nn},\chi_\text{nnn}\) are local, nearest-neighbour and next-nearest-neighbour correlation functions, with dispersions \(\xi_{\vec k} = 2\left[\cos(k_x a) + \cos\left(k_y a\right)\right] \) and \(\Xi_{\vec k} = 2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right] \). Following eqs.~\ref{local_correlation} through \ref{nnn_correlation}, these can be cast into impurity model correlation functions:
\begin{equation}\begin{aligned}
	\chi(\vec k)=& \frac{1}{2\lambda_{\vec k_0}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{W}}\braket{\mathcal{O}_1(z) \mathcal{O}_2(z)}_\text{aux}\right]\\
		    &+ \frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right] \\
		    &+ \frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right] 
\end{aligned}\end{equation}

@@

In Figs.~\ref{spin_kspace},\ref{charge_kspace} and \ref{pair_kspace}, we show the momentum dependence of two-particle correlation functions. In every figure, each panel shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\). Moving from the left panel to the right is equivalent to moving upwards in the top right quadrant of the first Brillouin zone. In each panel, moving upwards amounts to tuning the system towards the transition. The spin-spin correlations (in Fig.~\ref{spin_kspace}) are large near the \(\vec k = \left( 0,0 \right) \) point, presumably because of the dominance of the Kondo cloud at long wavelengths. They vanish in the local moment phase (flat blue region near the top). The charge and pairing correlations (Figs.~\ref{charge_kspace} and \ref{pair_kspace}) disappear as the system moves into the Kondo regime, but reappear exactly at the transition. This is tied to the non-Fermi liquid theory at the QCP, as seen in the auxiliary model.
\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{spin_rspace_all.pdf}
\caption{Momentum dependence of spin-spin correlation \(\left<\vec{S}_{-\vec k}\cdot\vec{S}_{\vec k} \right>\). Each frame shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\). Moving from the left figure to the right figure is equivalent to moving upwards in the top right quadrant of the first Brillouin zone. In each figure, moving upwards amounts to tuning the system towards the transition. The flat blue region at the top is the local moment phase, void of any non-local correlations.}
\label{spin_kspace}
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{charge_rspace_all.pdf}
\caption{Momentum dependence of charge-charge correlation \(\left<\vec{C}_{-\vec k}\cdot\vec{C}_{\vec k} \right>\), where \(\vec C\) is the charge isospin associated with the doublet formed by the doublon and holon states. Each frame shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\). Moving from the left figure to the right figure is equivalent to moving upwards in the top right quadrant of the first Brillouin zone. In each figure, moving upwards amounts to tuning the system towards the transition. The flat blue region at the top is the local moment phase, void of any non-local correlations.}
\label{charge_kspace}
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{pair_rspace_all.pdf}
\caption{Momentum dependence of pairing correlation \(\left<c^\dagger_{-k\uparrow}c^\dagger_{-k\downarrow}c_{k\downarrow}c_{k\uparrow}\right>\). Each frame shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\). Moving from the left figure to the right figure is equivalent to moving upwards in the top right quadrant of the first Brillouin zone. In each figure, moving upwards amounts to tuning the system towards the transition. The flat blue region at the top is the local moment phase, void of any non-local correlations.}
\label{pair_kspace}
\end{figure}
